---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SESverse

<!-- badges: start -->
<!-- badges: end -->

The goal of SESverse is to examine the flexibility of calculating Socioeconomic status in behaviour science literature.

## Installation

You can install the development version of SESverse like so:

``` r
install_github("Ziqian-xia/SESverse")
```

## Example

This is a basic example which shows you how to use this package.

Import the package:

```{r example}
library(SESverse)

```

Datasets are pre-loaded in the package for demo:

- CFPS 2010 Child
- PSID elderly

```{r results='hide'}
summary(CFPS_child)

summary(PSID_elderly)
```

There're many ways to calculate SES, we have coded them to make comparisons.

- Betan: Computation method of SES proposed by Betancourt, L, 2016
- More (Updating)

```{r CFPS, echo = T}

betan(faminc=50000,familysize = 5,edu_m = 12,method = 'raw',data = 'CFPS')

```

```{r PSID, echo = FALSE}

betan(faminc=50000,familysize = 5,edu_m = 12,method = 'raw',data = 'PSID')

```
